---
title: "Foundations of Data Analytics - HW 1"
author: "First Name - Last name - `flastname@floridapoly.edu`"
output: html_notebook
---

# Problem 1

Please enter your github repo address in the space provided below. I've added a little example to jog your memory.

>Example:  [My GitHub Link](TheGitHubLink.com)


> Enter Here: 
[My Git Hub Repo](https://github.com/Unpackwack/Homework-1-repo)

# Problem 2

For this problem, you are asked to create a list of **3 concepts** you have learned about so far this semester. Enter the solution below in the space provided.

a. Include the name of the course as a sub-heading (that is, using `##`)
## Foundations of Data Analytics

b. Include the concepts as an **unordered list** (This should not be done in a chunk of code, but simply inserted using markdown syntax). 
1. "collect"
2. "clean"
3. "analyze"

c. Include a link to information about at least one of the concept you listed (for example a link to the Wikipedia page about that concept/topics).
[careerfoundry.com](https://careerfoundry.com/en/blog/data-analytics/the-data-analysis-process-step-by-step/)


d. Include an an image that you think represents either one of the concepts or how you feel about one of the concepts. 

**Remember: you can also scan in and save something you've drawn or taken a picture of yourself.**

>Solution Below:
[Spreadsheet](Chart_illustration.png)

# Problem 3

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains your preferred name.

```{r}
# Solution for 3a:
my_name<-"Kevin"
```


(b)  Create a variable called `name_length` that holds how many letters are in `my_name`. Do not just set how many letters you have in your name to this variable, use a built-in function.

```{r}
# Solution for 3b:
name_length<-nchar(my_name)
```


(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 

> Hint: R has some built-in functions, `exp()` being one of them.

```{r}
# Solution for 3c:
exp(1)^pi
pi^exp(1)
print("exp(1)^pi is larger than pi^exp(1)")
```


(d) Define a **function** called `add_three` that takes a single argument and returns a value with 3 units added to the original input.

```{r}
# Solution for 3d:
add_three<-function(number){
  third_of_number<-number/3
  num1=third_of_number
  num2=third_of_number
  num3=third_of_number
  print(num3)
  #return(num1, num2, num3)
}
add_three(27)
```


(e)  Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.

```{r}
# Solution for 3e:
v<-10:49
length(v)
```

(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.

```{r}
# Solution for 3F:
seq(-5, 10, 0.5)
```


# Problem 4


(a) **Define a function** `imperial_to_metric` that takes in **two arguments**: a number of feet and a number of inches. The function should return the equivalent length in meters

> To convert a length `L` from feet (`ft`) and inches (`inches`) to meters (`m`), one can use the relation: `L(m) = L(ft) × 0.3048 + L(inches) × 0.0254`

```{r}
# insert code here - edit this comment
imperial_to_metric <- function(ft, inches) {
  meters<-(ft*0.348)+(inches*0.0254)
  return(cat(meters, "meters"))
}
```


(b) Create a variable `height_in_meters` by passing your height in imperial to the `imperial_to_metric` function.

```{r}
# insert code here - edit this comment
height_in_meters<-imperial_to_metric(5, 8)
```


# Problem 5

(a) Create the following vectors in `R` (see the pattern and use appropriate functions to construct these vectors):

$a = (5, 10, 15, 20, ..., 160)$

$b = (87, 86, 85, ..., 56)$


```{r}
# insert code here - edit this comment
vectors_by_5<-seq(5, 160, 5)
vectors_by_5

vectors_decreasing_by_1<-seq(87, 56, -1)
vectors_decreasing_by_1
```


(b) Multiply these vectors and call the result `d` (element-wise multiplication). 

```{r}
# insert code here - edit this comment
d <- vectors_by_5 * vectors_decreasing_by_1
d
```


(c) What are the 19th, 20th, and 21st elements of `d`?

```{r}
# insert code here - edit this comment
d[19]
d[20]
d[21]
```


(d) What are all of the elements of `d` which are less than 2000?

```{r}
# insert code here - edit this comment
for (element in d) {
 element
  if(element<2000){
    print(element)
  }
}
```


(e) How many elements of `d` are greater than 6000?


```{r}
# insert code here - edit this comment
greater_than_6000_value<-0
for(element in d){
  if(element>6000){
    greater_than_6000_value<-greater_than_6000_value+1
  }
}
print(greater_than_6000_value)
```


# Problem 6 - Word Problem

Assume that you have several investment choices. For each investment, there are two equally likely end-of-year forecasts: the optimistic value (up_value), and the pessimistic value (down_value). Assume the expected return and risk of each investment is given by:

> expected_end_value = (up_value + down_value) / 2 <br>
  expected_return = (expected_end_value - initial_investment) / initial_investment <br>
  risk = (up_value - down_value) / 2 <br>

a) Write a program that for one investment choice, prompts for three inputs:

- initial investment amount
- optimistic end value (up_value)
- pessimistic end value (down_value)

and then calculates the investment’s expected return and risk. You will need to enter your own chunks for this below:

```{r}
end_value_func<-function(ini_investment, upValue, downValue){
  expected_end_value<-(upValue+downValue)/2
  expected_return<-(expected_end_value-ini_investment)/ini_investment
  risk<-(upValue-downValue)/2
  return(cat("Your expected return is:", expected_return, "Your expected risk is:", risk))
}

input_investment<-as.numeric(readline("Initial Investment: "))
input_upValue<-as.numeric(readline("optimistic value end of year forcast: "))
input_downValue<-as.numeric(readline("pessimistic value end of year forcast: "))
end_value_func(input_investment, input_upValue, input_downValue)


```
